---
title: "TidyTueday_2019-50"
author: "Adrienne"
date: "December 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)

```

## Tidy Tuesday Week 50

# Workflow
Considering this is my first time trying a Tidy Tuesday project, I am going to take some notes about workflow so that I can refer back to them in the future. I'm currently working my way through David Robinson's screen casts of working through a Tidy Tuesday data set. 

There are a number of ways to bring in the data. I can copy and paste the code as I have done here. I can clone the repository (don't know how to do this yet, but I'm sure I'll figure it out). You can also get a URL from GitHub directly. If you click on the CSV file, it opens up the file into a screen with a URL and the raw data. That URL can be used with read_csv as I have done below.

Nice to see that I am doing things right by working in R projects and R Markdown.

```{r data-import}

murders <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/international_murders.csv")

gun_murders <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/gun_murders.csv")

diseases <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/diseases.csv")

nyc_regents <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/nyc_regents.csv")


```

``` {r summarize}

measles <- diseases %>%
  filter(disease == "Measles") %>%
  mutate(rate = (count/population * 100) * (52/weeks_reporting * 100)) %>%
  filter(!state == "Hawaii",
         !state == "Alaska") %>%
  mutate(state = reorder(state, desc(state)))

my.colors <- colorRampPalette(c("#f0ffff","#d0e9fb","#6ea6f0","#fbe204","#ffad00", "#fc2500", "#7f0d00"), bias = 2.4)

measles %>%
  ggplot(aes(year, state, fill = rate)) +
  geom_tile(width = .9, height = .9) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_fill_gradientn(colors = my.colors(18), na.value = "white") +
  geom_vline(xintercept = 1963) +
  ggtitle("Measles") +
  ylab("") +
  xlab("") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
     legend.position = "bottom", text = element_text(size = 8),
     plot.title = element_text(size = 12)) +
  annotate(geom = "text", x = 1963, y = 50.5, label = "Vaccine introduced", size = 3, hjust = 0)

ggsave("measles.jpg", width = 8, height = 6, units = "in")
```
Alright!  I like it. I still haven't figured out how to not cut off the top of my annotated words "Vaccine introduced", but that'll have to be for another time.  I also would go and work on the margins a bit more. I 
  
  I'm now thinking about how to convey some of my work data in this way, too. So it's been very helpful! 
