---
title: "TidyTueday_2019-50"
author: "Adrienne"
date: "December 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Tidy Tuesday Week 50

# Workflow
Considering this is my first time trying a Tidy Tuesday project, I am going to take some notes about workflow so that I can refer back to them in the future. I'm currently working my way through David Robinson's screen casts of working through a Tidy Tuesday data set. 

There are a number of ways to bring in the data. I can copy and paste the code as I have done here. I can clone the repository (don't know how to do this yet, but I'm sure I'll figure it out). You can also get a URL from GitHub directly. If you click on the CSV file, it opens up the file into a screen with a URL and the raw data. That URL can be used with read_csv as I have done below.

Nice to see that I am doing things right by working in R projects and R Markdown.

```{r data-import}

murders <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/international_murders.csv")

gun_murders <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/gun_murders.csv")

diseases <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/diseases.csv")

nyc_regents <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-10/nyc_regents.csv")


```

``` {r summarize}
diseases %>%
  view()

```