---
title: "TidyTuesday_2019_12_31"
author: "Adrienne"
date: "December 30, 2019"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(lubridate)

theme_set(theme_light())

```


```{r data import and clean}

christmas_songs <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-24/christmas_songs.csv")

christmas_lyrics <- readr::read_tsv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-24/christmas_lyrics.tsv")


christmas_songs <- christmas_songs %>%
  mutate(weekid = mdy(weekid))

```

```{r exploration}
head(christmas_lyrics)
head(christmas_songs)

summary(christmas_songs$year)
christmas_songs %>%
  count(songid, sort = T)

christmas_songs %>%
  ggplot(aes(month)) +
  geom_histogram(bins = 12)
  


```

Note that there are some mistakes in the data set. Some $ for S.  

Questions that arise:
How many new songs are released yearly?  
Which songs are still played years after they are released?
How many different musicians are popular within a given year?
What are the highest numbers of weeks on the charts for some songs?
How long do some Christmas songs last after Christmas?

I think we're going to find some surprises in here!


First, how many popular songs are there in a given year?

We saw from the histogram above, that the only months with data are November, December, and January. So. I could just consider the months of November and December and be fairly certain that I have captured that year's songs.
```{r}
songs_year <- christmas_songs %>%
                filter(month > 1) %>%
                select(songid, year) %>%
                count(year)

songs_year %>%
  ggplot(aes(year, n)) +
  geom_bar(stat = "identity") +
  ylab("number of popular Christmas songs")



```

First, how many new Christmas songs are released yearly?
I don't have data for the release date, so we will have to assume that the first time it's on the charts is the year it was released.
